\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-25 paper.tex
added getFromStore

    \noindent Applying the filter to the \textit{store} list will result in two outcomes. If the list is empty means that the variable does not exist and it can be safely put in the store. Thus, a tuple is returned containing the new \textit{Variable} and the modified store with the new \textit{Variable} included. Otherwise if the list is non empty then a tuple is returned containing a raised exception saying that the variable name already exists and the unmodified store as a result.

@@

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    getFromStore      :: String -> StateMonad (Exceptions Variable)
    getFromStore name = getStore `bindS` \store -> 
     case (filter (\v -> getVarName v == name ) store) of 
       []  -> returnS (raise ("variable " ++ name ++ " does not exist"))
    (x:xs) -> returnS (returnE x)

@@

    \noindent The \textbf{getFromStore} function is taking the name of the variable as a \textit{String} and a \textit{Store} to then return a tuple containing an Exception data type and the \textit{Store} (modified or not).

>>>>

    \noindent Applying the filter to the \textit{store} list will result in two outcomes. If the list is empty means that the variable does not exist and it can be safely put in the store. Thus, a tuple is returned containing the new \textit{Variable} and the modified store with the new \textit{Variable} included. Otherwise, if the list is non empty then a tuple is returned containing a raised exception saying that the variable name already exists and the unmodified store as a result.

@@

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    getFromStore      :: String -> StateMonad (Exceptions Variable)
    getFromStore name = \store -> 
    case (filter (\v -> getVarName v == name ) store) of 
    []  -> returnS (raise ("variable " ++ name 
                                       ++ " does not exist")) store 
    (x:xs) -> returnS (returnE x) store

@@

    \noindent The \textbf{getFromStore} function is taking the name of the variable as a \textit{String} and a \textit{Store} to then return a tuple containing an Exception data type and the unmodified \textit{Store}. As in the \textbf{putInStore} function, the \textit{Exception} data either raises an exception or returns a \textit{Variable}. The approach taken here is similar to the one taken when constructing the \textbf{putInStore} function, besides some modification to the outcomes of the \textbf{case of} construct. If an empty list is returned then a tuple is returned containing a raised exception saying that the variable requested does no exist and the unchanged store. Otherwise, if a list is non empty then a tuple is returned containing the corresponding \textit{Variable} returned and the unmodified store.
